PhD Title \\ PhD Thesis

### 2024-06-25 Latex_files/Thesis/chapters/chapter 3/main.tex
updates

\section{Optical Tweezer Equipment}
In general, all optical tweezers require a laser driver, two
microscope objectives (one for trapping and one for imaging),
and a means of controlling the position of the loaded sample. 
While there are other pieces of equipment used in modern tweezer
experiments these are the bare minimum requirements for any 
optical tweezer. The laser used for this project was a 1064 
nm near infrared laser - provided by CNI Lasers – that has 
an adjustable power supply to vary the energy output of the 
laser - the remaining optics where supplied by Thor Labs.
Experimental work has shown that the trapping efficiency 
increases with beam diameter up until it exceeds $\frac{2}{3}D_{obj}$ 
\cite{kim2003dependence} where $D_{obj}$ is the diameter
of the objective aperture. To expand the beam front we 
utilise a Galilean beam expansion arrangement (indicated 
by $L_1$, and $L_2$) as recommended for high power laser 
applications. In our initial experiments the beam expansion 
provides a $4\times$ magnification; however, in later experiments where we utilise a galvano-mirror the beam expansion is $3\times$ and then 
the 4f correlator provides a further $1.25\times$ magnification.
It should be noted that the galvano-mirror requires the use 
of a Keplerian beam expansion arrangement which reduces
the transmitted laser power due to localised heating of the air.
Afterwards the laser is passed through a dichroic mirror that 
separates incoming infrared and visible light, this is to 
prevent the laser from damaging the CCD camera used for imaging
the trapping plane. The laser is then focused to a diffraction
limited spot by a 1.25 NA objective. By increasing the numerical
aperture of the objective, the gradient force at the focal point is increased; the trade-off being that the for higher NA values the trapping depth 
is reduced due to spherical aberrations. While it is possible 
to increase the trapping depth \cite{Reihani2006} by adjusting 
the objective's tube length this approach is incompatible with 
our trapping arrangement. A 0.25 NA condenser objective refocuses
the scattered laser light and also provide an aperture for an 
imaging LED to illuminate the focal plane. Samples are loaded 
onto a piezo driven table to that is inserted between the trapping
and condensing objectives; the piezo drivers allow for sub-micron
control of the sample position to a degree as small as a 10 nm. 
To detect and monitor the position of a trapped particle a 
quadrant photo diode (QPD) was utilised.

\begin{figure}
	\centering
	\includegraphics[height=\linewidth, angle=270]{tweezer_setup.pdf}
	\caption{Optical tweezer set up used for the majority of the PhD. The focal lengths of $f_1$, $f_2$, $f_3$, \& $f_4$ are $-20\ mm$, $60\ mm$, $150\ mm$, \& $200\ mm$ respectively.}
\end{figure}

\subsection{Position detection methods}
In order to accurately capture the dynamics of a trapped particle, 
a position detection system must be utilised. As shown 
A QPD is a typical example of a position detection system commonly used 
in optical tweezers due to their high sampling rate, high degree of 
precision, and ease of set up. The QPD is constructed of four photo 
diodes assembled in a quadrant formation, when a particle is trapped the 
interference pattern produced is directed onto the QPD, with the maximum 
intensity mapping to the particle's centre of mass. By summing the 
horizontal and vertical quadrants together the particle's centre of mass 
is tracked in the x-y plane. While the tracking is accurate the QPD 
needs to be calibrated in order to convert the voltage signals into 
actual distance reading.

>>>>

\section{Optical Tweezer Equipment}
In general, all optical tweezers require a laser driver, two
microscope objectives (one for trapping and one for imaging),
and a means of controlling the position of the loaded sample. 
While there are other pieces of equipment used in modern tweezer
experiments these are the bare minimum requirements for any 
optical tweezer. The laser used for this project was a 1064 
nm near infrared laser - provided by CNI Lasers – that has 
an adjustable power supply to vary the energy output of the 
laser - the remaining optics where supplied by Thor Labs.
Experimental work has shown that the trapping efficiency 
increases with beam diameter up until it exceeds $\frac{2}{3}D_{obj}$ 
\cite{kim2003dependence} where $D_{obj}$ is the diameter
of the objective aperture. To expand the beam front we 
utilise a Galilean beam expansion arrangement (indicated 
by $f_1$, and $f_2$) as recommended for high power laser 
applications. In our initial experiments the beam expansion 
provides a $4\times$ magnification; however, in later experiments 
where we utilise a galvano-mirror the beam expansion is $3\times$ 
and then the 4f correlator provides a further $1.25\times$ magnification 
(using $f_3$ and $f_4$) - where the magnification is given by.
\begin{align}
	\frac{D_2}{D_1} = \frac{f_2}{f_1}
\end{align}
It should be noted that the galvano-mirror requires the use 
of a Keplerian beam expansion arrangement which reduces
the transmitted laser power due to localised heating of the air.
Afterwards the laser is passed through a dichroic mirror that 
separates incoming infrared and visible light, this is to 
prevent the laser from damaging the CCD camera used for imaging
the trapping plane. The laser is then focused to a diffraction
limited spot by a 1.25 NA objective. By increasing the numerical
aperture of the objective, the gradient force at the focal point 
is increased; the trade-off being that the for higher NA values 
the trapping depth is reduced due to spherical aberrations.
While it is possible to increase the trapping depth \cite{Reihani2006} 
by adjusting the objective's tube length this approach is incompatible 
with our trapping arrangement. A 0.25 NA condenser objective refocuses
the scattered laser light and also provide an aperture for an 
imaging LED to illuminate the focal plane. Samples are loaded 
onto a piezo driven table to that is inserted between the trapping
and condensing objectives; the piezo drivers allow for sub-micron
control of the sample position to a degree as small as a 10 nm. 
To detect and monitor the position of a trapped particle a 
quadrant photo diode (QPD) was utilised.

\begin{figure}
	\label{fig:setup}
	\centering
	\includegraphics[height=\linewidth, angle=270]{tweezer_setup.pdf}
	\caption{Optical tweezer set up used for the majority of the PhD. The focal lengths of $f_1$, $f_2$, $f_3$, \& $f_4$ are $-20\ mm$, $60\ mm$, $150\ mm$, \& $200\ mm$ respectively. Diagram not drawn to scale.}
\end{figure}

\subsection{Position detection methods}
In order to accurately capture the dynamics of a trapped particle, 
a position detection system must be utilised. While possible to characterise
an optical trap using a linear position detector
A QPD is a typical example of a position detection system commonly used 
in optical tweezers due to their high sampling rate, high degree of 
precision, and ease of set up. The QPD is constructed of four photo 
diodes assembled in a quadrant formation, when a particle is trapped the 
interference pattern produced is directed onto the QPD, with the maximum 
intensity mapping to the particle's centre of mass. By summing the 
horizontal and vertical quadrants together the particle's centre of mass 
is tracked in the x-y plane. While the tracking is accurate the QPD 
needs to be calibrated in order to convert the voltage signals into 
actual distance reading.
